---
title: "EIS SummeR Course"
author: "Kyle S. Yomogida"
date: "`r Sys.Date()`"
output: html_document
editor_options: 
  markdown: 
    wrap: 72
---

```{r}
library(table1)
library(tidyverse)
```

### Exercise Prompt -- Taken from SAS File

Exercise:

*Dataset: nat2018samp_exercise.csv;* Variables (range): id (generated):
ID MAGER: Mother's Single Years of Age (12-50) M_Ht_In: Mother's Height
in Total Inches (30-78) bmi: BMI (13-69.9, 99.9) PWgt_R: Pre-pregnancy
Weight Recode (75-375)\
DWgt_R: Delivery Weight Recode (100-400) WTGAIN: Weight Gain (0-98)
WTGAIN_REC: Weight Gain Recode (1-5) SEX: Sex of Infant (M/F) DBWT:
Birth Weight - Detail in Grams (0227-8165)

;

\*See
<https://ftp.cdc.gov/pub/Health_Statistics/NCHS/Dataset_Documentation/DVS/natality/UserGuide2018-508.pdf>
for more variable information;

```         
*1) Read in the dataset nat2018samp_exercise.csv and explore variables;



*2) Inspect dataset, keeping in mind types of potential errors:
    -out of range: do any records have values that are out of expected range?
    -errors of logic or consistency: are there any mismatches in variable values?
    -outliers/fringeliers: are there any (really/kind of) unusual values?
    -duplication: any records duplicated?;



*3) If you have time, correct any errors you find (you will need to make assumptions here) and 
    save your clean dataset for analysis;
```

## Prompt 1

*1) Read in the dataset nat2018samp_exercise.csv and explore variables*

```{r}
table1(~ ., data = nat2018samp_exercise)


```
